Hydra Battles and Cie

### 2020-12-28 doc/part-hydras.tex
minor modifications

The next chapter is dedicated to a generic implementation of ordinal notations, and chapter~\ref{chap:T1} to a proof of termination of all hydra battles with the help of an ordinal notation for the interval $[0,\epsilon_0)$.

@@

\noindent\emph{From Module~\href{../theories/html/hydras.OrdinalNotations.Generic.html}{OrdinalNotations.Generic}}
\begin{Coqsrc}
  Definition ZeroLimitSucc_dec {A:Type}{lt: relation A}
           {compare : A -> A -> comparison}
           {on : ON lt compare} :=
  forall alpha,
    {Least alpha} +
    {Limit alpha} +
    {beta: A | Successor alpha beta}.
(* ... *)
\end{Coqsrc}

@@

 Context (Hvar : Hvariant (Generic.wf (ON:=Omega2))  free m).
\end{Coqsrc}

@@

\begin{remark}
It is important to keep in mind  that the integer $n$ is not an ``element'' of \texttt{FinOrd $n$}. In set-theoretic presentations of ordinals, the set associated with the ordinal $n$ is $\{0,1,\dots,n-1\}$. 
In our formalization, the interpretation of an ordinal as a set is realized by the following definition
(in ~\href{../theories/html/hydras.OrdinalNotations.Generic.html}{OrdinalNotations.Generic}).

@@

In the module \href{../theories/html/hydras.Hydra.Epsilon0_Needed_Generic.html}{Hydra.Epsilon0\_Needed\_Generic}, we assume there exists some variant $m$ bounded by some ordinal $\mu<\epsilon_0$. This part of the development is parameterized by some class $B$ of battles, which will be instantiated later to \texttt{free} or \texttt{standard}.

@@

In the same way as for free battles, we import a large inequality 
from 
the module \href{../theories/html/hydras.Hydra.Epsilon0_Needed_Generic.html}{Hydra.Epsilon0\_Needed\_Generic}.

@@

On may ask whether the preceding results are not too restrictive, since they 
refer to a particular data type \texttt{T1}.
In fact, our representation of ordinals strictly less than 
 $\epsilon_0$ is faithful to their mathematical definition, at least 
Kurt Schütte's~\cite{schutte}, as proved in Chapter~\vref{chap:schutte}.
(please see also \href{../theories/html/hydras.Schutte.Correctness_E0.html}{the module \texttt{hydras.Schutte.Correctness\_E0}}).

>>>>

The next chapter is dedicated to a generic formalization of ordinal notations, and chapter~\ref{chap:T1} to a proof of termination of all hydra battles with the help of an ordinal notation for the interval $[0,\epsilon_0)$\,\footnote{We use the mathematical notation $[a,b)$ for the interval $\{x|a\leq x < b\}$.}.
\index{Maths!Notations!Interval}

@@

\noindent\emph{From Module~\href{../theories/html/hydras.OrdinalNotations.ON_Generic.html}{ON\_Generic}}
\begin{Coqsrc}
  Definition ZeroLimitSucc_dec {A:Type}{lt: relation A}
           {compare : A -> A -> comparison}
           {on : ON lt compare} :=
  forall alpha,
    {Least alpha} +
    {Limit alpha} +
    {beta: A | Successor alpha beta}.
(* ... *)
\end{Coqsrc}

@@

 Context (Hvar : Hvariant (ON_Generic.wf (ON:=Omega2))  free m).
\end{Coqsrc}

@@

\begin{remark}
It is important to keep in mind  that the integer $n$ is not an ``element'' of \texttt{FinOrd $n$}. In set-theoretic presentations of ordinals, the set associated with the ordinal $n$ is $\{0,1,\dots,n-1\}$. 
In our formalization, the interpretation of an ordinal as a set is realized by the following definition
(in ~\href{../theories/html/hydras.OrdinalNotations.ON_Generic.html}{ON\_Generic}).

@@

In the module \href{../theories/html/hydras.Hydra.Epsilon0_Needed_Generic.html}{Epsilon0\_Needed\_Generic}, we assume there exists some variant $m$ bounded by some ordinal $\mu<\epsilon_0$. This part of the development is parameterized by some class $B$ of battles, which will be instantiated later to \texttt{free} or \texttt{standard}.

@@

In the same way as for free battles, we import a large inequality 
from 
the module \href{../theories/html/hydras.Hydra.Epsilon0_Needed_Generic.html}{Epsilon0\_Needed\_Generic}.

@@

On may ask whether the preceding results are too restrictive, since they 
refer to a particular data type \texttt{T1}.
In fact, our representation of ordinals strictly less than 
 $\epsilon_0$ is faithful to their mathematical definition, at least 
Kurt Schütte's~\cite{schutte}, as proved in Chapter~\vref{chap:schutte}.
(please see also \href{../theories/html/hydras.Schutte.Correctness_E0.html}{the module \texttt{hydras.Schutte.Correctness\_E0}}).
